---
title: "Publications"
editor: visual
citation_package: biblatex
citecolor: "red"
date: "2023-03-31"
date-modified: last-modified
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bib2df)
library(knitr)
library(kableExtra)
library(formattable)
library(dplyr)
library(wordcloud)
library(RColorBrewer)
library(wordcloud2)
```

```{r cloudWord, echo = FALSE, warning = FALSE, message = FALSE}
set.seed(18792)
bib_df <- bib2df("./GiulianosPubs.bib", separate_names = TRUE)

myPub <- bib_df %>% 
  filter(NOTE == "Peer-reviewed") %>% 
  select("TITLE", "YEAR", "MONTH","AUTHOR", "JOURNAL", "CATEGORY",
          "DOI", "VOLUME", "NUMBER", "PAGES", "NOTE", "KEYWORDS")
textCloud <- unlist(strsplit(myPub$KEYWORDS, ","))
textCloud <- as.data.frame(table(textCloud))
textCloud <- textCloud[order(textCloud$Freq, decreasing = T), ]
colnames(textCloud) <- c("word", "freq")       
wordcloud2(textCloud)
```

<br>

The above word-cloud shows the keywords associated with my publications. A complete list of all my publications is presented below, organized in different tables: peer reviewed pubs (including accepted manuscripts that are currently undergoing the publication process); pubs that are still through the review process; manuscripts that are about to be submitted to a scientific journal or are still in the making; other more general publications including my PhD dissertation and my MS thesis. The title of each publication is actually a link to either the official journal web-page where it was published or to a repository where you can find a PDF copy of it. If the link doesn't work (or currently is not available) the cell will have a gold-ish background color. Manuscripts in review or that are still in the making have a orange or forest green color, respectively, and the link will take you nowhere unless there is a preview version of the draft. I periodically check these lists and the link to make sure that it is up to date.

## Peer reviewed (published/accepted)

```{r peerreviewed, echo = FALSE, warning = FALSE, message = FALSE}
bib_df <- bib2df("./GiulianosPubs.bib", separate_names = TRUE)

myPub <- bib_df %>% 
  filter(NOTE == "Peer-reviewed") %>% 
  select("TITLE", "YEAR", "MONTH","AUTHOR", "JOURNAL", "CATEGORY",
          "DOI", "VOLUME", "NUMBER", "PAGES", "NOTE")

myPub$YEAR[myPub$YEAR == "2009}"] <- 2009
myPub$YEAR[myPub$YEAR == "2016}"] <- 2016
myPub$YEAR[myPub$YEAR == "2020}"] <- 2020
myPub$YEAR[myPub$YEAR == "2021}"] <- 2021
myPub$YEAR[myPub$YEAR == "2022}"] <- 2022
myPub$YEAR[myPub$YEAR == "2023}"] <- 2023
myPub$YEAR[myPub$YEAR == "2024}"] <- 2024
myPub$YEAR <- as.numeric(myPub$YEAR)
myPub$MONTH <- as.numeric(myPub$MONTH)
myPub <- myPub[order(myPub$YEAR, myPub$MONTH, decreasing = T), ]
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){x[,c("last_name", "first_name")]})
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){
  paste(x[,"last_name"],
        substr(x[,"first_name"],1,1))
})

myPub$AUTHOR <- lapply(myPub$AUTHOR, function(y){unlist(lapply(y, function(x){if (x == "Colosimo G"){
  paste("<b>", x, "</b>", sep = "")
} else {
  x
}}))})

myPub$AUTHOR <- unlist(lapply(myPub$AUTHOR, paste, collapse = ", "))
myPub$TITLE <- text_spec(myPub$TITLE, link = myPub$DOI, format = "html",
                         color = "blue")

myPub$JOURNAL <- apply(myPub[, c("JOURNAL", "VOLUME", "PAGES")], 1,
      function(x){
        Selector <- as.matrix(x)
        Selector <- !is.na(Selector)
        paste(x[Selector], collapse = ", ")
      })

myPub$COUNT <- rev(seq(1:nrow(myPub)))

linkColor <- ifelse(is.na(myPub$DOI), "gold", "")

kable(myPub[, c("COUNT","YEAR", "MONTH", "TITLE", "AUTHOR", "JOURNAL")], format = "html", escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                font_size = 7) %>%
  column_spec(1, bold = F, width = "5em", border_right = T) %>%
  column_spec(2, bold = F, width = "5em", border_right = T) %>%
  column_spec(3, bold = F, width = "5em", border_right = T) %>%
  column_spec(4, width = "40em", border_right = T, background = linkColor) %>%
  column_spec(5, width = "25em", border_right = T) %>%
  column_spec(6, width = "10em", color = "red")
```

## In review

```{r inreview, echo = FALSE, warning = FALSE, message = FALSE, eval=TRUE}
bib_df <- bib2df("./GiulianosPubs.bib", separate_names = TRUE)

myPub <- bib_df %>% 
  filter(NOTE == "In review") %>% 
  select("TITLE", "YEAR", "AUTHOR", "JOURNAL", "CATEGORY",
          "DOI", "VOLUME", "NUMBER", "PAGES", "NOTE")

myPub$YEAR[myPub$YEAR == "2009}"] <- 2009
myPub$YEAR[myPub$YEAR == "2016}"] <- 2016
myPub$YEAR[myPub$YEAR == "2020}"] <- 2020
myPub$YEAR[myPub$YEAR == "2021}"] <- 2021
myPub$YEAR[myPub$YEAR == "2022}"] <- 2022
myPub$YEAR[myPub$YEAR == "2023}"] <- 2023
myPub$YEAR[myPub$YEAR == "2024}"] <- 2024
myPub$YEAR[myPub$YEAR == "2025}"] <- 2025
myPub$YEAR <- as.numeric(myPub$YEAR)
myPub <- myPub[order(myPub$YEAR, decreasing = T), ]
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){x[,c("last_name", "first_name")]})
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){
  paste(x[,"last_name"],
        substr(x[,"first_name"],1,1))
})

myPub$AUTHOR <- lapply(myPub$AUTHOR, function(y){unlist(lapply(y, function(x){if (x == "Colosimo G"){
  paste("<b>", x, "</b>", sep = "")
} else {
  x
}}))})

myPub$AUTHOR <- unlist(lapply(myPub$AUTHOR, paste, collapse = ", "))
myPub$TITLE <- text_spec(myPub$TITLE, link = myPub$DOI, format = "html",
                         color = "blue")

myPub$JOURNAL <- apply(myPub[, c("JOURNAL", "VOLUME", "PAGES")], 1,
      function(x){
        Selector <- as.matrix(x)
        Selector <- !is.na(Selector)
        paste(x[Selector], collapse = ", ")
      })

myPub$COUNT <- rev(seq(1:nrow(myPub)))

linkColor <- ifelse(is.na(myPub$DOI), "orange", "")

kable(myPub[, c("COUNT","YEAR", "TITLE", "AUTHOR", "JOURNAL")], format = "html", escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                font_size = 7) %>%
  column_spec(1, bold = F, width = "5em", border_right = T) %>%
  column_spec(2, bold = F, width = "5em", border_right = T) %>%
  column_spec(3, width = "40em", border_right = T, background = linkColor) %>%
  column_spec(4, width = "25em", border_right = T) %>%
  column_spec(5, width = "10em",color = "red")

```

## In preparation

```{r inprep, echo = FALSE, warning = FALSE, message = FALSE, eval=TRUE}
bib_df <- bib2df("./GiulianosPubs.bib", separate_names = TRUE)

myPub <- bib_df %>% 
  filter(NOTE == "In preparation") %>% 
  select("TITLE", "YEAR", "AUTHOR", "JOURNAL", "CATEGORY",
          "DOI", "VOLUME", "NUMBER", "PAGES", "NOTE")

myPub$YEAR[myPub$YEAR == "2009}"] <- 2009
myPub$YEAR[myPub$YEAR == "2016}"] <- 2016
myPub$YEAR[myPub$YEAR == "2020}"] <- 2020
myPub$YEAR[myPub$YEAR == "2021}"] <- 2021
myPub$YEAR[myPub$YEAR == "2022}"] <- 2022
myPub$YEAR[myPub$YEAR == "2023}"] <- 2023
myPub$YEAR[myPub$YEAR == "2024}"] <- 2024
myPub$YEAR[myPub$YEAR == "2025}"] <- 2025
myPub$YEAR <- as.numeric(myPub$YEAR)
myPub <- myPub[order(myPub$YEAR, decreasing = T), ]
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){x[,c("last_name", "first_name")]})
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){
  paste(x[,"last_name"],
        substr(x[,"first_name"],1,1))
})

myPub$AUTHOR <- lapply(myPub$AUTHOR, function(y){unlist(lapply(y, function(x){if (x == "Colosimo G"){
  paste("<b>", x, "</b>", sep = "")
} else {
  x
}}))})

myPub$AUTHOR <- unlist(lapply(myPub$AUTHOR, paste, collapse = ", "))
myPub$TITLE <- text_spec(myPub$TITLE, link = myPub$DOI, format = "html",
                         color = "gold")

myPub$JOURNAL <- apply(myPub[, c("JOURNAL", "VOLUME", "PAGES")], 1,
      function(x){
        Selector <- as.matrix(x)
        Selector <- !is.na(Selector)
        paste(x[Selector], collapse = ", ")
      })

myPub$COUNT <- rev(seq(1:nrow(myPub)))

linkColor <- ifelse(is.na(myPub$DOI), "forestgreen", "")

kable(myPub[, c("COUNT","YEAR", "TITLE", "AUTHOR", "JOURNAL")], format = "html", escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                font_size = 7) %>%
  column_spec(1, bold = F, width = "5em", border_right = T) %>%
  column_spec(2, bold = F, width = "5em", border_right = T) %>%
  column_spec(3, width = "40em", border_right = T, background = linkColor) %>%
  column_spec(4, width = "25em", border_right = T) %>%
  column_spec(5, width = "10em",color = "red")



```


## Non peer reviewed

```{r nonpeereviewed, echo = FALSE, warning = FALSE, message = FALSE}
bib_df <- bib2df("./GiulianosPubs.bib", separate_names = TRUE)

myPub <- bib_df %>% 
  filter(NOTE == "Non Peer-reviewed") %>% 
  select("TITLE", "YEAR", "AUTHOR",
          "DOI", "VOLUME", "NUMBER", "PAGES", "NOTE")

myPub$YEAR[myPub$YEAR == "2009}"] <- 2009
myPub$YEAR[myPub$YEAR == "2016}"] <- 2016
myPub$YEAR[myPub$YEAR == "2020}"] <- 2020
myPub$YEAR[myPub$YEAR == "2022}"] <- 2022
myPub$YEAR[myPub$YEAR == "2023}"] <- 2023
myPub$YEAR[myPub$YEAR == "2024}"] <- 2024
myPub$YEAR <- as.numeric(myPub$YEAR)
myPub <- myPub[order(myPub$YEAR, decreasing = T), ]
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){x[,c("last_name", "first_name")]})
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){
  paste(x[,"last_name"],
        substr(x[,"first_name"],1,1))
})

myPub$AUTHOR <- lapply(myPub$AUTHOR, function(y){unlist(lapply(y, function(x){if (x == "Colosimo G"){
  paste("<b>", x, "</b>", sep = "")
} else {
  x
}}))})

myPub$AUTHOR <- unlist(lapply(myPub$AUTHOR, paste, collapse = ", "))
myPub$TITLE <- text_spec(myPub$TITLE, link = myPub$DOI, format = "html",
                         color = "blue")

myPub$COUNT <- rev(seq(1:nrow(myPub)))

linkColor <- ifelse(is.na(myPub$DOI), "gold", "")

kable(myPub[, c("COUNT","YEAR", "TITLE", "AUTHOR")], format = "html", escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                font_size = 7) %>%
  column_spec(1, bold = F, width = "5em", border_right = T) %>%
  column_spec(2, bold = F, width = "5em", border_right = T) %>%
  column_spec(3, width = "40em", border_right = T, background = linkColor) %>%
  column_spec(4, width = "25em", border_right = T)
```
