---
title: "Publications"
editor: visual
citation_package: biblatex
citecolor: "red"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bib2df)
library(knitr)
library(kableExtra)
library(formattable)
library(dplyr)
```

## Peer reviewed

This is a list of all my peer reviewed publications, from the most recent to the oldest ones. If you click on the title you should be redirected to the specific journal web-page or to a readable version of the manuscript. If you are interested in any specific publication, but do not have direct access to it (some of them are not in an open-access format) feel free to contact me and I will get back to you with the publication as soon as possible.


```{r peerreviewed, echo = FALSE, warning = FALSE, message = FALSE}
bib_df <- bib2df("./GiulianosPubs.bib", separate_names = TRUE)

myPub <- bib_df %>% 
  filter(NOTE == "Peer-reviewed") %>% 
  select("TITLE", "YEAR", "AUTHOR", "JOURNAL", "CATEGORY",
          "DOI", "VOLUME", "NUMBER", "PAGES", "NOTE")

myPub$YEAR[myPub$YEAR == "2009}"] <- 2009
myPub$YEAR[myPub$YEAR == "2016}"] <- 2016
myPub$YEAR[myPub$YEAR == "2020}"] <- 2020
myPub$YEAR[myPub$YEAR == "2021}"] <- 2021
myPub$YEAR[myPub$YEAR == "2022}"] <- 2022
myPub$YEAR[myPub$YEAR == "2023}"] <- 2023
myPub$YEAR <- as.numeric(myPub$YEAR)
myPub <- myPub[order(myPub$YEAR, decreasing = T), ]
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){x[,c("last_name", "first_name")]})
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){
  paste(x[,"last_name"],
        substr(x[,"first_name"],1,1))
})

myPub$AUTHOR <- lapply(myPub$AUTHOR, function(y){unlist(lapply(y, function(x){if (x == "Colosimo G"){
  paste("<b>", x, "</b>", sep = "")
} else {
  x
}}))})

myPub$AUTHOR <- unlist(lapply(myPub$AUTHOR, paste, collapse = ", "))
myPub$TITLE <- text_spec(myPub$TITLE, link = myPub$DOI, format = "html",
                         color = "blue")

myPub$JOURNAL <- apply(myPub[, c("JOURNAL", "VOLUME", "PAGES")], 1,
      function(x){
        Selector <- as.matrix(x)
        Selector <- !is.na(Selector)
        paste(x[Selector], collapse = ", ")
      })

myPub$COUNT <- rev(seq(1:nrow(myPub)))

kable(myPub[, c("COUNT","YEAR", "TITLE", "AUTHOR", "JOURNAL")], format = "html", escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                font_size = 7) %>%
  column_spec(1, bold = F, width = "5em", border_right = T) %>%
  column_spec(2, bold = F, width = "5em", border_right = T) %>%
  column_spec(3, width = "40em", border_right = T) %>%
  column_spec(4, width = "25em", border_right = T) %>%
  column_spec(5, width = "10em",color = "red")
```


## Non Peer-reviewed

Here is a list of publications that did not undergo the peer review process for publication. Some of them are manuscripts that I am currently working on, others are the result of other projects that I have been involved in. There are also references to articles that have been published to reach out to the wider public. You will also find the references to my master and PhD thesis, as well as the reference of other thesis of students that I have mentored/tutored throughout their academic career.

```{r nonpeereviewed, echo = FALSE, warning = FALSE, message = FALSE}
bib_df <- bib2df("./GiulianosPubs.bib", separate_names = TRUE)

myPub <- bib_df %>% 
  filter(NOTE == "Non Peer-reviewed") %>% 
  select("TITLE", "YEAR", "AUTHOR",
          "DOI", "VOLUME", "NUMBER", "PAGES", "NOTE")

myPub$YEAR[myPub$YEAR == "2009}"] <- 2009
myPub$YEAR[myPub$YEAR == "2016}"] <- 2016
myPub$YEAR[myPub$YEAR == "2020}"] <- 2020
myPub$YEAR[myPub$YEAR == "2022}"] <- 2022
myPub$YEAR[myPub$YEAR == "2023}"] <- 2023
myPub$YEAR <- as.numeric(myPub$YEAR)
myPub <- myPub[order(myPub$YEAR, decreasing = T), ]
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){x[,c("last_name", "first_name")]})
myPub$AUTHOR <- lapply(myPub$AUTHOR, function(x){
  paste(x[,"last_name"],
        substr(x[,"first_name"],1,1))
})

myPub$AUTHOR <- lapply(myPub$AUTHOR, function(y){unlist(lapply(y, function(x){if (x == "Colosimo G"){
  paste("<b>", x, "</b>", sep = "")
} else {
  x
}}))})

myPub$AUTHOR <- unlist(lapply(myPub$AUTHOR, paste, collapse = ", "))
myPub$TITLE <- text_spec(myPub$TITLE, link = myPub$DOI, format = "html",
                         color = "blue")

myPub$COUNT <- rev(seq(1:nrow(myPub)))

kable(myPub[, c("COUNT","YEAR", "TITLE", "AUTHOR")], format = "html", escape = F) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),
                font_size = 7) %>%
  column_spec(1, bold = F, width = "5em", border_right = T) %>%
  column_spec(2, bold = F, width = "5em", border_right = T) %>%
  column_spec(3, width = "40em", border_right = T) %>%
  column_spec(4, width = "25em", border_right = T)
```


