---
title: "data.table joins I always re-look-up"
date: 2026-09-23
categories: ["R", "data.table", "wrangling"]
description: "Left, anti, rolling and update joins in data.table syntax."
---

## Why

`dplyr` join names are verbs; `data.table` joins are punctuation. This is the
translation table I keep reopening.

## Left join

```{r, echo=TRUE, eval=FALSE}
library(data.table)

# All rows of x, matching columns from y
y[x, on = .(id)]

# Equivalent, more explicit
merge(x, y, by = "id", all.x = TRUE)
```

## Anti join

```{r, echo=TRUE, eval=FALSE}
# Rows of x with no match in y
x[!y, on = .(id)]
```

## Update by reference

The one that makes `data.table` worth it — add columns from `y` into `x`
without copying.

```{r, echo=TRUE, eval=FALSE}
x[y, on = .(id), `:=`(score = i.score, label = i.label)]
```

`i.` prefixes the column from the *second* table in the join.

## Rolling join

Match each row of `x` to the most recent earlier row of `y`.

```{r, echo=TRUE, eval=FALSE}
setkey(y, id, date)
y[x, on = .(id, date), roll = TRUE]

# Only roll forward up to 7 days
y[x, on = .(id, date), roll = 7]
```

## Non-equi join

```{r, echo=TRUE, eval=FALSE}
# Every event in y falling inside x's window
y[x, on = .(id, date >= start, date <= end)]
```
